Windowed least-squares model reduction for dynamical systems

### 2019-10-12 main.tex
address comments and appendix 3

	\KTC{In this section, $a$ and $b$ are sometimes used as time limits, while
	$0$ and $T$ are used elsewhere. Please go through carefully and make this
	consistent. I recommend using $a$ and $b$ because this is used within time
	windows.}
	\KTC{In this section, "extremum" is used a lot. You are just finding
	stationary points, which could be local minima, local maxima, or saddle
	points. Please avoid using "extemum" for this reason.} 

@@

\mathcal{J}: (\statey,\stateyDot) \mapsto  \int_0^T \integrand(\statey(t),\stateyDot(t),t)  dt,

@@

where $\integrand: \RR{M}  \times \RR{M}  \times[0,T] \rightarrow  \RRplus$

@@

	the function $\statez: [0,T] \rightarrow \RR{M}$ that is implicitly defined
	as an extremum of~\eqref{eq:el_gen} subject to the boundary condition
	$\statez(0) = \statez_0$. \KTC{This previous sentence isn't correct. The

@@

	evaluated at the time-dependent function and its derivative..} 
We introduce an arbitrary function $\variation : [0,T] \rightarrow \RR{M}$
with the boundary condition $\variationArg{0} = \bz$ and define a variation
from the extremum by

@@

We note that $\statezBar$ satisfies the same boundary condition $\statez$ since $\variationArg{0} = \bz$.

@@

\int_0^T \bigg[ \frac{\partial \integrand  }{\partial \stateyDiscrete } \big(\statezBar(t,\epsilon),\statezDotBar(t,\epsilon) ,t\big) \frac{\partial \statezBar }{\partial \delta}(t,\epsilon)  + \frac{\partial \integrand}{\partial \stateyDotDiscrete } \big(\statezBar(t,\epsilon),\statezDotBar(t,\epsilon) ,t \big) \frac{\partial \statezDotBar}{\partial \delta} (t,\epsilon)\bigg]dt . $$

@@

= \int_0^T \bigg[ \frac{\partial \integrand  }{\partial \stateyDiscrete } \big(\statezBar(t,\epsilon),\statezDotBar(t,\epsilon),t \big) \variation(t)  + \frac{\partial \integrand}{\partial \stateyDotDiscrete } \big(\statezBar(t,\epsilon),\statezDotBar(t,\epsilon) ,t \big) \variationDot(t) \bigg]dt. $$

@@

	=&  \int_0^T  \bigg[\frac{\partial \integrand  }{\partial \stateyDiscrete }

@@

	,t \big) \bigg) \variation(t) \bigg]dt + \\ &\frac{\partial \integrand}{\partial \stateyDotDiscrete} \big(\statezBar(T,\epsilon),\statezDotBar(T,\epsilon) ,T \big) \variation(T) . 

@@

where we have used $\variationArg{0} = \bz$.

@@

  \int_0^T  \bigg[\frac{\partial \integrand  }{\partial \stateyDiscrete } \big(\statezBar(t,\epsilon),\statezDotBar(t,\epsilon),t \big) \variation(t) - \frac{d}{dt}\bigg( \frac{\partial \integrand}{\partial \stateyDotDiscrete }  \big(\statezBar(t,\epsilon),\statezDotBar(t,\epsilon),t \big) \bigg) \variation(t) \bigg]dt + \frac{\partial \integrand}{\partial \stateyDotDiscrete} \big(\statezBar(T,\epsilon),\statezDotBar(T,\epsilon),T \big) \variation(T)  = 0. 

@@

By construction, $\statez(\cdot) \equiv \statezBar(\cdot;0)$ is a stationary

@@

  \int_0^T  \bigg[\frac{\partial \integrand  }{\partial \stateyDiscrete } \big(\statez(t),\statezDot(t),t \big) \variation(t) - \frac{d}{dt}\bigg( \frac{\partial \integrand}{\partial \stateyDotDiscrete }  \big(\statez(t),\statezDot(t),t \big) \bigg) \variation(t) \bigg]dt + \frac{\partial \integrand}{\partial \stateyDotDiscrete} \big(\statez(T),\statezDot(T) ,T\big) \variation(T)  = 0. 

@@

\statez(a) = \statez_a, \qquad \bigg[ \frac{\partial \integrand}{\partial \stateyDotDiscrete} \big(\statez(b),\statezDot(b),b \big) \variation(b) \bigg]^T = \bz.

@@

of $a$, $b$, and $0$, $T$.}

@@

equation. It states that, if $\statez$ is an extremum of $\mathcal{J}$
\KTC{Again, note that $\mathcal J$ has two arguments, so it can't havec a
single vector servec as an extremum. Fix needed}, then it must

@@

that~\eqref{eq:euler_lagrange_appendix} is a necessary condition on $\statez$

@@

stationary point of $\mathcal{J}$, but the resulting stationary point can be
either a maximum or a minimum. \KTC{See above. Strictly, these could be local
minima, local maxima, or saddle points.}

>>>>

@@

\mathcal{J}: (\statey,\stateyDot) \mapsto  \int_a^b \integrand(\statey(t),\stateyDot(t),t)  dt,

@@

where $\integrand: \RR{M}  \times \RR{M}  \times[a,b] \rightarrow  \RRplus$

@@

	the function $\statez: [a,b] \rightarrow \RR{M}$ with $\statez: \timeDummy \mapsto \statez(\timeDummy)$ along with $\statezDot \equiv d \statez /d\timeDummy$. We define this function to be a stationary point of~\eqref{eq:el_gen} (with $\statez$ being the first argument and $\statezDot$ being the second argument) subject to the boundary condition
	$\statez(a) = \statez_a$. \KTC{This previous sentence isn't correct. The

@@

	evaluated at the time-dependent function and its derivative..}\EP{ Check this, I think this is more precise now.} 
We introduce an arbitrary function $\variation : [a,b] \rightarrow \RR{M}$
with the boundary condition $\variationArg{a} = \bz$ and define a variation
from the stationary point by

@@

We note that $\statezBar$ satisfies the same boundary condition $\statez$ since $\variationArg{a} = \bz$.

@@

\int_a^b \bigg[ \frac{\partial \integrand  }{\partial \stateyDiscrete } \big(\statezBar(t,\epsilon),\statezDotBar(t,\epsilon) ,t\big) \frac{\partial \statezBar }{\partial \delta}(t,\epsilon)  + \frac{\partial \integrand}{\partial \stateyDotDiscrete } \big(\statezBar(t,\epsilon),\statezDotBar(t,\epsilon) ,t \big) \frac{\partial \statezDotBar}{\partial \delta} (t,\epsilon)\bigg]dt . $$

@@

= \int_a^b \bigg[ \frac{\partial \integrand  }{\partial \stateyDiscrete } \big(\statezBar(t,\epsilon),\statezDotBar(t,\epsilon),t \big) \variation(t)  + \frac{\partial \integrand}{\partial \stateyDotDiscrete } \big(\statezBar(t,\epsilon),\statezDotBar(t,\epsilon) ,t \big) \variationDot(t) \bigg]dt. $$

@@

	=&  \int_a^b  \bigg[\frac{\partial \integrand  }{\partial \stateyDiscrete }

@@

	,t \big) \bigg) \variation(t) \bigg]dt + \\ &\frac{\partial \integrand}{\partial \stateyDotDiscrete} \big(\statezBar(b,\epsilon),\statezDotBar(b,\epsilon) ,b \big) \variation(b) , 

@@

where we have used $\variationArg{a} = \bz$.

@@

  \int_a^b  \bigg[\frac{\partial \integrand  }{\partial \stateyDiscrete } \big(\statezBar(t,\epsilon),\statezDotBar(t,\epsilon),t \big) \variation(t) - \frac{d}{dt}\bigg( \frac{\partial \integrand}{\partial \stateyDotDiscrete }  \big(\statezBar(t,\epsilon),\statezDotBar(t,\epsilon),t \big) \bigg) \variation(t) \bigg]dt + \frac{\partial \integrand}{\partial \stateyDotDiscrete} \big(\statezBar(b,\epsilon),\statezDotBar(b,\epsilon),b \big) \variation(b)  = 0. 

@@

By construction, $\statez(\cdot) \equiv \statezBar(\cdot;0)$ and $\statezDot(\cdot) \equiv \statezDotBar(\cdot;0)$, comprise a stationary

@@

  \int_a^b  \bigg[\frac{\partial \integrand  }{\partial \stateyDiscrete } \big(\statez(t),\statezDot(t),t \big) \variation(t) - \frac{d}{dt}\bigg( \frac{\partial \integrand}{\partial \stateyDotDiscrete }  \big(\statez(t),\statezDot(t),t \big) \bigg) \variation(t) \bigg]dt + \frac{\partial \integrand}{\partial \stateyDotDiscrete} \big(\statez(b),\statezDot(b) ,b\big) \variation(b)  = 0. 

@@

\statez(a) = \statez_a, \qquad \bigg[ \frac{\partial \integrand}{\partial \stateyDotDiscrete} \big(\statez(b),\statezDot(b),b \big) \bigg]^T = \bz.

@@

of $a$, $b$, and $0$, $T$.} \EP{Yes, sorry about the [a,b], I changed this recently and obviously missed things. As for the BC, 
the requirement that $z(a)=z_a$ comes in first from the implicit definition of $z$, which is required to satisfy this BC. Then, in defining the variation, 
we explicitly force the variation to be zero at the IC such that all possible functions satisfy the BC. We don't, however, make any such requirement on the end point 
condition, $\eta(b)$ can be anything. This yields the endpoint boundary condition on the gradient (i.e., second term in Eq 56.). If we had a fixed final boundary condition, then the second term in Eq. 56 would be replaced 
with this end point condition.} 

@@

equation. It states that, for ($\statez$,$\statezDot$) to define a stationary point of $\mathcal{J}$, then they must 

@@

that~\eqref{eq:euler_lagrange_appendix} is a necessary condition on ($\statez,\statezDot$)

@@

stationary point of $\mathcal{J}$, but the resulting stationary point could be a local minima, local maxima, or saddle point.
